Week2 - Descriptives

### 2024-09-14 week2.Rmd
week2 edits

text here \$ N = ß \Sigma lss \sqrt {sd } \$ text again

@@

# START WRITING INTRO (UPDATE RESEARCH QUESTIONS)

@@

MAKE A LISTOFTHE TYPE OF DATA YOU WILL NEED Relational attributes, etc.

@@

[USING THE REFERENCES]{.underline}

Open: references.bib take "bibTex Citation" if you want to use it, use \@ - symbol and use the word behind the { \
In this example, it would be \@ "rmarkdown2018" (without the quotation marks

>>>>

@@

# HW: START WRITING INTRO (UPDATE RESEARCH QUESTIONS)

@@

MAKE A LIST OF THE TYPE OF DATA YOU WILL NEED Relational attributes, etc.

@@

Also still redo what i missed in class: make centrality measures of the 10x10 matrix

text here
$$
N = ß \Sigma lss \sqrt {sd }
$$
text again

text here
$$
N = 1 
$$
text again

# USING THE REFERENCES

Open: references.bib

take "bibTex Citation" from online and put it in there

if you want to use it, use \@ - symbol and use the word behind the " { "\
In this example, it would be \@ "rmarkdown2018" (without the quotation marks)
